Complementary Filters Shaping Using $\mathcal{H}_\infty$ Synthesis

### 2019-10-30 poster/ligo.tex
Update poster
Reworked the minipage setup
Poster: Update part about H-infinity synthesis

\textbf{Control Configuration}

\begin{minipage}[t]{0.49\linewidth}
  \begin{tikzfigure}[Specifications and weighting functions magnitude used for $\mathcal{H}_\infty$ synthesis]
    \label{fig:ligo_weights}
    \centering
    \includegraphics[scale=1.8]{figs/ligo_weights.pdf}
  \end{tikzfigure}
\end{minipage}\hfill
\begin{minipage}[t]{0.49\linewidth}
  \begin{tikzfigure}[Comparison of the FIR filters (solid) designed in \cite{hua05_low_ligo} with the filters obtained with $\mathcal{H}_\infty$ synthesis (dashed)]
    \label{fig:comp_fir_ligo_hinf}
    \centering
    \includegraphics[scale=1.8]{figs/comp_fir_ligo_hinf.pdf}
  \end{tikzfigure}
\end{minipage}

>>>>

%%% Local Variables:
%%% TeX-master: "poster"
%%% End:

The specifications for one pair of complementary filters used at the LIGO are
detailed in \cite{hua04_polyp_fir_compl_filter_contr_system} and shown in the
frequency domain in Fig.~\ref{fig:ligo_weights}.

\begin{minipage}[t]{0.49\linewidth}
  \begin{tikzfigure}[Specifications and weighting functions magnitude used for $\mathcal{H}_\infty$ synthesis]
    \label{fig:ligo_weights}
    \centering
    \includegraphics[width=\linewidth]{figs/ligo_weights.pdf}
  \end{tikzfigure}
\end{minipage}\hfill
\begin{minipage}[t]{0.49\linewidth}
  \begin{tikzfigure}[Comparison of the FIR filters (solid) designed in \cite{hua05_low_ligo} with the filters obtained with $\mathcal{H}_\infty$ synthesis (dashed)]
    \label{fig:comp_fir_ligo_hinf}
    \centering
    \includegraphics[width=\linewidth]{figs/comp_fir_ligo_hinf.pdf}
  \end{tikzfigure}
\end{minipage}
